formula1

### 2020-07-20 inst/f1points.Rmd
typo

\begin{itemize}
\item Equal points to the top $n$ competitors
$(\underbrace{1,1,\ldots ,1}_{r},0,0,\ldots)$, noting that
$n=r$ corresponds to a ``winner takes all'' system
\item Linear decrease $(r,r-1,r-2,\ldots,3,2,1,0)$ for integer $0<r<n$
\item Exponential decay $(1,r,r^2,r^3,\ldots)$ for some fixed $r<1$
\item Zipf's law $(1,1/2,1/3,1/4,\ldots)$
\item The current Formula 1 system $(25,18,15,12,10,8,6,4,2,1)$
\item The inaugural Formula 1 system $(8,6,4,3,2)$
\end{itemize}

>>>>

\begin{itemize}
\item Equal points to the top $r$ competitors
$(\underbrace{1,1,\ldots ,1}_{r},0,0,\ldots)$, noting that
$r=1$ corresponds to a ``winner takes all'' system
\item Linear decrease $(r,r-1,r-2,\ldots,3,2,1,0)$ for integer $0<r<n$
\item Exponential decay $(1,r,r^2,r^3,\ldots)$ for some fixed $r<1$
\item Zipf's law $(1,1/2,1/3,1/4,\ldots)$
\item The current Formula 1 system $(25,18,15,12,10,8,6,4,2,1)$
\item The inaugural Formula 1 system $(8,6,4,3,2)$
\end{itemize}
